---
title: "pwfsl-uptime-report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE)
```

# Background

This is a report that assesses the current status of all PWFSL web services
related to the [PWFSL Monitoring V4](https://tools.airfire.org/monitoring/v4) site.

# Plot Service

San Francisco

 * <https://tools-c2.airfire.org/monitor-plot/v4/plot?databaseversion=4.0&webserviceapi=4.0&plottype=timeseries&monitorid=060750005_01>
 * <https://tools-c3.airfire.org/monitor-plot/v4/plot?databaseversion=4.0&webserviceapi=4.0&plottype=timeseries&monitorid=060750005_01>
 * <https://tools-c5.airfire.org/monitor-plot/v4/plot?databaseversion=4.0&webserviceapi=4.0&plottype=timeseries&monitorid=060750005_01>

```{r plot-service}
# TODO:  Iterate through all servers (i.e. c2, c3, c5)
# TODO:  Request the product
# TODO:   * test that the product is of the correct type
# TODO:   * keep track of response time
# TODO:   * display table of status/response time
# TODO:   * could also display images in the table
# TODO:  
# TODO:  Thinking ahead, what would be needed to send an alert message to Slack
# TODO:  if anything failed?
```

# Map Service

San Francisco

 * <https://tools-c2.airfire.org/monitor-map/v4/monitorlocation?maptype=roadmap&monitorid=060750005_01>
 * <https://tools-c3.airfire.org/monitor-map/v4/monitorlocation?maptype=roadmap&monitorid=060750005_01>
 * <https://tools-c5.airfire.org/monitor-map/v4/monitorlocation?maptype=roadmap&monitorid=060750005_01>

```{r map-service}
# TODO:  Iterate through all servers (i.e. c2, c3, c5)
# TODO:  Request the product
# TODO:   * test that the product is of the correct type
# TODO:   * keep track of response time
# TODO:   * display table of status/response time
# TODO:   * could also display images in the table
# TODO:  
# TODO:  Thinking ahead, what would be needed to send an alert message to Slack
# TODO:  if anything failed?
```

# Data Service

San Francisco

 * <https://tools-c2.airfire.org/monitor-data/v4/data?databaseversion=4.0&webserviceapi=4.0&monitors=060750005_01&outputfiletype=text&lookbackdays=2>
 * <https://tools-c3.airfire.org/monitor-data/v4/data?databaseversion=4.0&webserviceapi=4.0&monitors=060750005_01&outputfiletype=text&lookbackdays=2>
 * <https://tools-c5.airfire.org/monitor-data/v4/data?databaseversion=4.0&webserviceapi=4.0&monitors=060750005_01&outputfiletype=text&lookbackdays=2>

```{r data-service}
# TODO:  Iterate through all servers (i.e. c2, c3, c5)
# TODO:  Request the product
# TODO:   * test that the product is of the correct type
# TODO:   * keep track of response time
# TODO:   * display table of status/response time
# TODO:   * could also display images in the table
# TODO:  
# TODO:  Thinking ahead, what would be needed to send an alert message to Slack
# TODO:  if anything failed?
```

# Data-Report Service

San Francisco

 * <https://tools-c2.airfire.org/monitor-data-report/v4/report?databaseversion=4.0&webserviceapi=4.0&monitors=060750005_01&>
 * <https://tools-c3.airfire.org/monitor-data-report/v4/report?databaseversion=4.0&webserviceapi=4.0&monitors=060750005_01&>
 * <https://tools-c5.airfire.org/monitor-data-report/v4/report?databaseversion=4.0&webserviceapi=4.0&monitors=060750005_01&>

```{r data-report-service}
# TODO:  Iterate through all servers (i.e. c2, c3, c5)
# TODO:  Request the product
# TODO:   * test that the product is of the correct type
# TODO:   * keep track of response time
# TODO:   * display table of status/response time
# TODO:   * could also display images in the table
# TODO:  
# TODO:  Thinking ahead, what would be needed to send an alert message to Slack
# TODO:  if anything failed?
```

# Daily-Hourly Service

San Francisco

*NOTE: This is running on tools-c4*

 * <https://tools-c4.airfire.org/monitor-custom/v1/dailyhourlybarplot?outputfiletype=pdf&lookbackdays=10&monitors=060750005_01&>


```{r daily-hourly-service}
# TODO:  Iterate through all servers (i.e. c2, c3, c5)
# TODO:  Request the product
# TODO:   * test that the product is of the correct type
# TODO:   * keep track of response time
# TODO:   * display table of status/response time
# TODO:   * could also display images in the table
# TODO:  
# TODO:  Thinking ahead, what would be needed to send an alert message to Slack
# TODO:  if anything failed?
```

# QC-Report Service

King’s Canyon temporary monitor

 * <https://tools-c2.airfire.org/monitor-qc-report/v4/airsis?databaseversion=4.0&webserviceapi=4.0&provider=apcd&unitID=1033>
 * <https://tools-c3.airfire.org/monitor-qc-report/v4/airsis?databaseversion=4.0&webserviceapi=4.0&provider=apcd&unitID=1033>
 * <https://tools-c5.airfire.org/monitor-qc-report/v4/airsis?databaseversion=4.0&webserviceapi=4.0&provider=apcd&unitID=1033>


```{r qc-report-service}
# TODO:  Iterate through all servers (i.e. c2, c3, c5)
# TODO:  Request the product
# TODO:   * test that the product is of the correct type
# TODO:   * keep track of response time
# TODO:   * display table of status/response time
# TODO:   * could also display images in the table
# TODO:  
# TODO:  Thinking ahead, what would be needed to send an alert message to Slack
# TODO:  if anything failed?
```

# Monitoring UI

 * <https://tools-c2.airfire.org/monitoring/v4>
 * <https://tools-c3.airfire.org/monitoring/v4>
 * <https://tools-c5.airfire.org/monitoring/v4>
 
```{r monitoring-ui}
# TODO:  Iterate through all servers (i.e. c2, c3, c5)
# TODO:  Request the product
# TODO:   * test that the product is of the correct type
# TODO:   * keep track of response time
# TODO:   * display table of status/response time
# TODO:   * could also display images in the table
# TODO:  
# TODO:  Thinking ahead, what would be needed to send an alert message to Slack
# TODO:  if anything failed?
```


